### 2018-09-10 Sections/about_the_authors.tex
Some new stubs
Adding image cropping

\begin{center}
\includegraphics[width=0.47\textwidth]{photo_peter_rohde}
\end{center}

@@

\begin{center}
\includegraphics[width=0.47\textwidth]{photo_heliang_huang}
\end{center}

@@

\begin{center}
\includegraphics[width=0.47\textwidth]{photo_zuen_su}
\end{center}

@@

\begin{center}
\includegraphics[width=0.47\textwidth]{photo_zixin_huang}
\end{center}

@@

\begin{center}
\includegraphics[width=0.47\textwidth]{photo_chris_ferrie}
\end{center}

@@

\begin{center}
\includegraphics[width=0.47\textwidth]{photo_simon_devitt}
\end{center}

@@

\begin{center}
\includegraphics[width=0.47\textwidth]{photo_sihui_tan}
\end{center}

@@

\begin{center}
\includegraphics[width=0.47\textwidth]{photo_nana_liu}
\end{center}

@@

\begin{center}
\includegraphics[width=0.47\textwidth]{photo_ryan_mann}
\end{center}

Ryan Mann is a PhD candidate in the Centre for Quantum Software \& Information at the University of Technology Sydney. He is a better rock-climber than he is physicist, despite being outstanding at the latter.

@@

\begin{center}
\includegraphics[width=0.47\textwidth]{photo_rohit_ramakrishnan}
\end{center}

@@

\begin{center}
\includegraphics[width=0.47\textwidth]{photo_jon_dowling}
\end{center}

@@

\begin{center}
\includegraphics[width=0.47\textwidth]{photo_tim_byrnes}
\end{center}

@@

\begin{center}
\includegraphics[width=0.47\textwidth]{photo_bill_munro}
\end{center}

>>>>

\begin{center}
\includegraphics[clip=true, width=0.475\textwidth]{photo_peter_rohde}
\end{center}

@@

\begin{center}
\includegraphics[clip=true, width=0.475\textwidth]{photo_heliang_huang}
\end{center}

@@

\begin{center}
\includegraphics[clip=true, width=0.475\textwidth]{photo_zuen_su}
\end{center}

@@

\begin{center}
\includegraphics[clip=true, width=0.475\textwidth]{photo_zixin_huang}
\end{center}

@@

\begin{center}
\includegraphics[clip=true, width=0.475\textwidth]{photo_chris_ferrie}
\end{center}

@@

\begin{center}
\includegraphics[clip=true, width=0.475\textwidth]{photo_simon_devitt}
\end{center}

@@

\begin{center}
\includegraphics[clip=true, width=0.475\textwidth]{photo_sihui_tan}
\end{center}

@@

\begin{center}
\includegraphics[clip=true, width=0.475\textwidth]{photo_nana_liu}
\end{center}

@@

%\begin{center}
%\includegraphics[clip=true, width=0.475\textwidth]{photo_ryan_mann}
%\end{center}

%Ryan Mann is a PhD candidate in the Centre for Quantum Software \& Information at the University of Technology Sydney. He is a better rock-climber than he is physicist, despite being outstanding at the latter.

%\comment{Complete this section}

@@

\begin{center}
\includegraphics[clip=true, width=0.475\textwidth]{photo_rohit_ramakrishnan}
\end{center}

@@

\begin{center}
\includegraphics[clip=true, width=0.475\textwidth]{photo_jon_dowling}
\end{center}

@@

\begin{center}
\includegraphics[clip=true, width=0.475\textwidth]{photo_tim_byrnes}
\end{center}

@@

\begin{center}
\includegraphics[clip=true, width=0.475\textwidth]{photo_bill_munro}
\end{center}

### 2018-09-10 Sections/economics_of_the_quantum_internet.tex
minor
Adding image cropping

The exact form of the scaling function will be specific to the algorithm being deployed\footnote{For example, the \textit{circuit depth}\index{Circuit depth}, i.e number of gate applications in series, will heavily influence the number of classical steps required to simulate the circuit.}, and the computational model (e.g cluster states vs the circuit model, as well as choices in error correction, amongst other factors). Most notably, different quantum algorithms offer different scalings in their quantum speedup -- Grover's algorithm (Sec.~\ref{sec:quantum_search})\index{Grover's algorithm} offers only a quadratic quantum speedup, compared to the exponential speedup afforded by Shor's algorithm (Sec.~\ref{sec:shors_alg})\index{Shor's algorithm}. Thus, the computational scaling function depends on both the hardware and software, and may therefore differ between different users operating the same computer.

@@

\begin{figure}[htb!]\index{Network price scaling factor}
	\includegraphics[width=0.475\textwidth]{network_price_scaling_factor}
	\captionspacefig \caption{Network price scaling factor, $\chi_\mathrm{sc}$, as a function of several representative computational scaling functions, $f_\mathrm{sc}$, where $n$ is network size.} \label{fig:NPSF}
\end{figure}

@@

\begin{figure}[!htbp]
	\includegraphics[width=0.4\textwidth]{network_value}
	\captionspacefig \caption{Dollar value (in units of \mbox{$C_0N_0$}) of the network as a function of time, growth rate in the number of physical qubits, and rate of decay in the dollar value of physical qubits. When \mbox{$\gamma_N/\gamma_C=1$} the network's value remains constant over time. Above this the network's value appreciates exponentially, and below which it depreciates exponentially against time.} \label{fig:network_value}
\end{figure}

@@

\if 2\pubmode
\begin{figure}[!htbp]
\includegraphics[width=0.4\textwidth]{cost_of_comp_n}\\
\includegraphics[width=0.4\textwidth]{cost_of_comp_n2}\\
\includegraphics[width=0.4\textwidth]{cost_of_comp_2n}
\captionspacefig \caption{Examples of the temporal dynamics of the cost of computation for different scaling functions and exponential growth rates. Units are \mbox{$C_0=N_0=n=1$}, with RoR \mbox{$\gamma_\mathrm{ror}=0$}. A non-zero RoR would simply scale these figures by a constant factor of $e^{\gamma_\mathrm{ror}}$.}\label{fig:econ_cost_of_comp}
\end{figure}
\else
\begin{figure*}[!htbp]
\includegraphics[width=0.325\textwidth]{cost_of_comp_n}
\includegraphics[width=0.325\textwidth]{cost_of_comp_n2}
\includegraphics[width=0.325\textwidth]{cost_of_comp_2n}
\captionspacefig \caption{Examples of the temporal dynamics of the cost of computation for different scaling functions and exponential growth rates. Units are \mbox{$C_0=N_0=n=1$}, with RoR \mbox{$\gamma_\mathrm{ror}=0$}. A non-zero RoR would simply scale these figures by a constant factor of $e^{\gamma_\mathrm{ror}}$.}\label{fig:econ_cost_of_comp}
\end{figure*}
\fi

@@

\begin{figure}[!htbp]
\includegraphics[width=0.475\textwidth]{single_qubit_QCL}
\captionspacefig \caption{Time-dependent quantum computational leverage for a single qubit (\mbox{$n=1$}) with different computational scaling functions, under the assumption of exponential network growth in units of \mbox{$N_0=1$}.}\label{fig:time_dep_QCL}
\end{figure}

@@

\if 2\pubmode
\begin{figure}[!htbp]
\includegraphics[width=0.4\textwidth]{forward_cont_pricing_mod_1}\\
\includegraphics[width=0.4\textwidth]{forward_cont_pricing_mod_2}
\captionspacefig \caption{Forward price on a computation to be delivered at time $T$ in the future, in units \mbox{$C_0=N_0=1$}, where we are assuming an exponential scaling function, \mbox{$f_\mathrm{sc}(n)=e^n$}.}\label{fig:forward_cont_pricing_mod}
\end{figure}
\else
\begin{figure*}[!htbp]
\includegraphics[width=0.475\textwidth]{forward_cont_pricing_mod_1}
\includegraphics[width=0.475\textwidth]{forward_cont_pricing_mod_2}
\captionspacefig \caption{Forward price on a computation to be delivered at time $T$ in the future, in units \mbox{$C_0=N_0=1$}, where we are assuming an exponential scaling function, \mbox{$f_\mathrm{sc}(n)=e^n$}.}\label{fig:forward_cont_pricing_mod}
\end{figure*}
\fi

@@

\begin{figure}[!htbp]
\includegraphics[width=0.475\textwidth]{quantcoin_protocol}
\captionspacefig \caption{Flowchart for the QuantCoin\texttrademark\, protocol, introduced in Alg.~\ref{alg:quant_coin}.}\label{fig:quantcoin_protocol}	
\end{figure}

@@

\if 2\pubmode
\begin{figure}[!htbp]
\includegraphics[width=0.475\textwidth]{tax_exp}\\
\includegraphics[width=0.475\textwidth]{tax_subsidy}
\captionspacefig \caption{(top) Relationship between the tax performance multiplier, (positive) tax rate, and network size, assuming an exponential computational scaling function, in the regime of positive taxation, \mbox{$\gamma_T>1$}. (bottom) For \mbox{$N_\mathrm{tax}=10$}, a zoom into the region around neutral taxation, where \mbox{$\gamma_T\approx 1$}, showing slight degrees of both taxation (\mbox{$\gamma_T>1$}) and subsidisation (\mbox{$\gamma_T<1$}). Neutral taxation, \mbox{$\gamma_T=1$}, is shown in orange.}\label{fig:tax_exp}\index{Tea party}\index{Don't tread on me}
\end{figure}
\else
\begin{figure*}[!htbp]
\includegraphics[width=0.475\textwidth]{tax_exp}
\includegraphics[width=0.475\textwidth]{tax_subsidy}
\captionspacefig \caption{(left) Relationship between the tax performance multiplier, (positive) tax rate, and network size, assuming an exponential computational scaling function, in the regime of positive taxation, \mbox{$\gamma_T>1$}. (right) For \mbox{$N_\mathrm{tax}=10$}, a zoom into the region around neutral taxation, where \mbox{$\gamma_T\approx 1$}, showing slight degrees of both taxation (\mbox{$\gamma_T>1$}) and subsidisation (\mbox{$\gamma_T<1$}). Neutral taxation, \mbox{$\gamma_T=1$}, is shown in orange.}\label{fig:tax_exp}\index{Tea party}\index{Don't tread on me}
\end{figure*}
\fi

@@

\if 2\pubmode
\begin{figure}[!htbp]
\includegraphics[width=0.45\textwidth]{supply_demand_long}
\captionspacefig \caption{Hypothetical supply/demand curves, showing the impact of taxation on price and supply, for both inelastic (a) and elastic (b) market dynamics. $Q_e$ and $P_e$ are the efficient market quantity and price of the asset respectively. $P_s$ is the price faced by suppliers, while $P_c$ is the consumer price under taxation. $Q_t$ is the quantity in a taxed environment. The net tax revenue collected is shaded in light teal, and the loss of market efficiency through the imposition of taxation is shaded in dark teal.}\index{Supply \& demand curve}\label{fig:supply_demand}	
\end{figure}
\else
\begin{figure*}[!htbp]
\includegraphics[width=0.8\textwidth]{supply_demand}
\captionspacefig \caption{Hypothetical supply/demand curves, showing the impact of taxation on price and supply, for both inelastic (a) and elastic (b) market dynamics. $Q_e$ and $P_e$ are the efficient market quantity and price of the asset respectively. $P_s$ is the price faced by suppliers, while $P_c$ is the consumer price under taxation. $Q_t$ is the quantity in a taxed environment. The net tax revenue collected is shaded in light teal, and the loss of market efficiency through the imposition of taxation is shaded in dark teal.}\index{Supply \& demand curve}\label{fig:supply_demand}	
\end{figure*}
\fi

>>>>

The exact form of the scaling function will be specific to the algorithm being deployed\footnote{For example, the \textit{circuit depth}\index{Circuit depth}, i.e number of gate applications in series, will heavily influence the number of classical steps required to simulate the circuit.}, and the computational model (e.g cluster states vs the circuit model, as well as choices in error correction, amongst other factors). Most notably, different quantum algorithms offer different scalings in their quantum speedup -- Grover's algorithm (Sec.~\ref{sec:quantum_search})\index{Grover's algorithm} offers only a quadratic quantum speedup, compared to the exponential speedup afforded by Shor's algorithm (Sec.~\ref{sec:shors_alg})\index{Shor's algorithm}. Thus, the computational scaling function depends on both the hardware and software, and may therefore differ between different users operating the same computer. We abstract this away and assume all these factors and resource overheads have been merged into the scaling function.

@@

\begin{figure}[htb!]\index{Network price scaling factor}
	\includegraphics[clip=true, width=0.475\textwidth]{network_price_scaling_factor}
	\captionspacefig \caption{Network price scaling factor, $\chi_\mathrm{sc}$, as a function of several representative computational scaling functions, $f_\mathrm{sc}$, where $n$ is network size.} \label{fig:NPSF}
\end{figure}

@@

\begin{figure}[!htbp]
	\includegraphics[clip=true, width=0.4\textwidth]{network_value}
	\captionspacefig \caption{Dollar value (in units of \mbox{$C_0N_0$}) of the network as a function of time, growth rate in the number of physical qubits, and rate of decay in the dollar value of physical qubits. When \mbox{$\gamma_N/\gamma_C=1$} the network's value remains constant over time. Above this the network's value appreciates exponentially, and below which it depreciates exponentially against time.} \label{fig:network_value}
\end{figure}

@@

\if 2\pubmode
\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.4\textwidth]{cost_of_comp_n}\\
\includegraphics[clip=true, width=0.4\textwidth]{cost_of_comp_n2}\\
\includegraphics[clip=true, width=0.4\textwidth]{cost_of_comp_2n}
\captionspacefig \caption{Examples of the temporal dynamics of the cost of computation for different scaling functions and exponential growth rates. Units are \mbox{$C_0=N_0=n=1$}, with RoR \mbox{$\gamma_\mathrm{ror}=0$}. A non-zero RoR would simply scale these figures by a constant factor of $e^{\gamma_\mathrm{ror}}$.}\label{fig:econ_cost_of_comp}
\end{figure}
\else
\begin{figure*}[!htbp]
\includegraphics[clip=true, width=0.325\textwidth]{cost_of_comp_n}
\includegraphics[clip=true, width=0.325\textwidth]{cost_of_comp_n2}
\includegraphics[clip=true, width=0.325\textwidth]{cost_of_comp_2n}
\captionspacefig \caption{Examples of the temporal dynamics of the cost of computation for different scaling functions and exponential growth rates. Units are \mbox{$C_0=N_0=n=1$}, with RoR \mbox{$\gamma_\mathrm{ror}=0$}. A non-zero RoR would simply scale these figures by a constant factor of $e^{\gamma_\mathrm{ror}}$.}\label{fig:econ_cost_of_comp}
\end{figure*}
\fi

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{single_qubit_QCL}
\captionspacefig \caption{Time-dependent quantum computational leverage for a single qubit (\mbox{$n=1$}) with different computational scaling functions, under the assumption of exponential network growth in units of \mbox{$N_0=1$}.}\label{fig:time_dep_QCL}
\end{figure}

@@

\if 2\pubmode
\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.4\textwidth]{forward_cont_pricing_mod_1}\\
\includegraphics[clip=true, width=0.4\textwidth]{forward_cont_pricing_mod_2}
\captionspacefig \caption{Forward price on a computation to be delivered at time $T$ in the future, in units \mbox{$C_0=N_0=1$}, where we are assuming an exponential scaling function, \mbox{$f_\mathrm{sc}(n)=e^n$}.}\label{fig:forward_cont_pricing_mod}
\end{figure}
\else
\begin{figure*}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{forward_cont_pricing_mod_1}
\includegraphics[clip=true, width=0.475\textwidth]{forward_cont_pricing_mod_2}
\captionspacefig \caption{Forward price on a computation to be delivered at time $T$ in the future, in units \mbox{$C_0=N_0=1$}, where we are assuming an exponential scaling function, \mbox{$f_\mathrm{sc}(n)=e^n$}.}\label{fig:forward_cont_pricing_mod}
\end{figure*}
\fi

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{quantcoin_protocol}
\captionspacefig \caption{Flowchart for the QuantCoin\texttrademark\, protocol, introduced in Alg.~\ref{alg:quant_coin}.}\label{fig:quantcoin_protocol}	
\end{figure}

@@

\if 2\pubmode
\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{tax_exp}\\
\includegraphics[clip=true, width=0.475\textwidth]{tax_subsidy}
\captionspacefig \caption{(top) Relationship between the tax performance multiplier, (positive) tax rate, and network size, assuming an exponential computational scaling function, in the regime of positive taxation, \mbox{$\gamma_T>1$}. (bottom) For \mbox{$N_\mathrm{tax}=10$}, a zoom into the region around neutral taxation, where \mbox{$\gamma_T\approx 1$}, showing slight degrees of both taxation (\mbox{$\gamma_T>1$}) and subsidisation (\mbox{$\gamma_T<1$}). Neutral taxation, \mbox{$\gamma_T=1$}, is shown in orange.}\label{fig:tax_exp}\index{Tea party}\index{Don't tread on me}
\end{figure}
\else
\begin{figure*}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{tax_exp}
\includegraphics[clip=true, width=0.475\textwidth]{tax_subsidy}
\captionspacefig \caption{(left) Relationship between the tax performance multiplier, (positive) tax rate, and network size, assuming an exponential computational scaling function, in the regime of positive taxation, \mbox{$\gamma_T>1$}. (right) For \mbox{$N_\mathrm{tax}=10$}, a zoom into the region around neutral taxation, where \mbox{$\gamma_T\approx 1$}, showing slight degrees of both taxation (\mbox{$\gamma_T>1$}) and subsidisation (\mbox{$\gamma_T<1$}). Neutral taxation, \mbox{$\gamma_T=1$}, is shown in orange.}\label{fig:tax_exp}\index{Tea party}\index{Don't tread on me}
\end{figure*}
\fi

@@

\if 2\pubmode
\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.45\textwidth]{supply_demand_long}
\captionspacefig \caption{Hypothetical supply/demand curves, showing the impact of taxation on price and supply, for both inelastic (a) and elastic (b) market dynamics. $Q_e$ and $P_e$ are the efficient market quantity and price of the asset respectively. $P_s$ is the price faced by suppliers, while $P_c$ is the consumer price under taxation. $Q_t$ is the quantity in a taxed environment. The net tax revenue collected is shaded in light teal, and the loss of market efficiency through the imposition of taxation is shaded in dark teal.}\index{Supply \& demand curve}\label{fig:supply_demand}	
\end{figure}
\else
\begin{figure*}[!htbp]
\includegraphics[clip=true, width=0.8\textwidth]{supply_demand}
\captionspacefig \caption{Hypothetical supply/demand curves, showing the impact of taxation on price and supply, for both inelastic (a) and elastic (b) market dynamics. $Q_e$ and $P_e$ are the efficient market quantity and price of the asset respectively. $P_s$ is the price faced by suppliers, while $P_c$ is the consumer price under taxation. $Q_t$ is the quantity in a taxed environment. The net tax revenue collected is shaded in light teal, and the loss of market efficiency through the imposition of taxation is shaded in dark teal.}\index{Supply \& demand curve}\label{fig:supply_demand}	
\end{figure*}
\fi

### 2018-09-10 Sections/encrypted_cloud_quantum_computing.tex
Adding image cropping

\begin{figure}[!htbp]
\includegraphics[width=0.425\textwidth]{gen_pass_hom}
\captionspacefig \caption{General structure for the relationship between the encoding ($\hat{E}$), decoding ($\hat{D}$), and computational ($\hat{U}$) operations in a passive, non-interactive, optical quantum computation, where Alice is restricted to non-entangling, single-mode encoding and decoding operations.} \label{fig:gen_pass_hom}
\end{figure}

@@

\begin{figure}[!htbp]
\includegraphics[width=0.425\textwidth]{BS_homo}
\captionspacefig \caption{Protocol for implementing homomorphic encryption on photonic passive linear optics. Horizontal bars are wave-plates, implementing polarisation rotations $\hat{R}(\theta)$ -- the encryption and decryption operations performed by Alice. $\ket\psi_\mathrm{in}$ contains one photon per mode, polarisation-encoded such that vertically polarised photons belong to the desired computation, whilst the remaining horizontally polarised ones are dummies. The polarisation rotation angle, $k$, acts as Alice's private key. The photo-detectors are polarisation-resolving, discarding all dummy horizontally polarised photons at the output. The algorithm is described in detail in Alg.~\ref{alg:homo_LO}.} \label{fig:BS_homo}
\end{figure}

@@

\if 2\pubmode
\begin{figure}[!htbp]
\includegraphics[width=0.475\textwidth]{coherent_state_homo_unenc}\\
\includegraphics[width=0.475\textwidth]{coherent_state_homo_enc}
\captionspacefig \caption{Trace distance between unencoded (top) and encoded (bottom) basis states for coherent state computation using phase-key encoding, with \mbox{$d=50$} keys and \mbox{$m=10$} modes. Each mode is inputted with one of two basis coherent states, \mbox{$\ket{\pm\alpha}$}. \mbox{$\mathrm{wt}(\vec{x})$} denotes the Hamming weight of bit-string $\vec{x}$. Two states are indistinguishable if their trace distance is 0, and distinguishable (orthogonal) if their trace distance is 1. Lower trace distance between encoded states implies a lower chance of Bob guessing Alice's plaintext input state.} \label{fig:homo_coh_st_tr}
\end{figure}
\else
\begin{figure*}[!htbp]
\includegraphics[width=0.475\textwidth]{coherent_state_homo_unenc}
\includegraphics[width=0.475\textwidth]{coherent_state_homo_enc}
\captionspacefig \caption{Trace distance between unencoded (top) and encoded (bottom) basis states for coherent state computation using phase-key encoding, with \mbox{$d=50$} keys and \mbox{$m=10$} modes. Each mode is inputted with one of two basis coherent states, \mbox{$\ket{\pm\alpha}$}. \mbox{$\mathrm{wt}(\vec{x})$} denotes the Hamming weight of bit-string $\vec{x}$. Two states are indistinguishable if their trace distance is 0, and distinguishable (orthogonal) if their trace distance is 1. Lower trace distance between encoded states implies a lower chance of Bob guessing Alice's plaintext input state.} \label{fig:homo_coh_st_tr}
\end{figure*}
\fi

\begin{figure}[!htbp]
\includegraphics[width=0.475\textwidth]{coherent_state_homo_ratio}
\captionspacefig \caption{Ratio of the trace distance between unencoded and encoded basis states for coherent state computation using phase-key encoding, with \mbox{$d=50$} keys and \mbox{$m=10$} modes. \mbox{$R<1$} implies information hiding from Bob.} \label{fig:homo_coh_st_ratio}
\end{figure}

@@

\begin{figure}[!htbp]
\includegraphics[width=0.475\textwidth]{lo_displacement_homo}
\captionspacefig \caption{Circuit layout for displacement-key homomorphic encoding of passive linear optics, where \mbox{$\alpha_i'=\alpha_i/r$} and \mbox{$\beta_i'=\beta_i/r$}. Mixing the input modes with respective coherent states on a very low-reflectivity ($r$) beamsplitter implements the displacement operations. Following decoding, the output states is simply given by \mbox{$\ket{\psi_\mathrm{out}} = \hat{U}\ket{\psi_\mathrm{in}}$}, the computed input state.}\label{fig:lo_disp_key_circuit}	
\end{figure}

>>>>

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.425\textwidth]{gen_pass_hom}
\captionspacefig \caption{General structure for the relationship between the encoding ($\hat{E}$), decoding ($\hat{D}$), and computational ($\hat{U}$) operations in a passive, non-interactive, optical quantum computation, where Alice is restricted to non-entangling, single-mode encoding and decoding operations.} \label{fig:gen_pass_hom}
\end{figure}

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.425\textwidth]{BS_homo}
\captionspacefig \caption{Protocol for implementing homomorphic encryption on photonic passive linear optics. Horizontal bars are wave-plates, implementing polarisation rotations $\hat{R}(\theta)$ -- the encryption and decryption operations performed by Alice. $\ket\psi_\mathrm{in}$ contains one photon per mode, polarisation-encoded such that vertically polarised photons belong to the desired computation, whilst the remaining horizontally polarised ones are dummies. The polarisation rotation angle, $k$, acts as Alice's private key. The photo-detectors are polarisation-resolving, discarding all dummy horizontally polarised photons at the output. The algorithm is described in detail in Alg.~\ref{alg:homo_LO}.} \label{fig:BS_homo}
\end{figure}

@@

\if 2\pubmode
\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{coherent_state_homo_unenc}\\
\includegraphics[clip=true, width=0.475\textwidth]{coherent_state_homo_enc}
\captionspacefig \caption{Trace distance between unencoded (top) and encoded (bottom) basis states for coherent state computation using phase-key encoding, with \mbox{$d=50$} keys and \mbox{$m=10$} modes. Each mode is inputted with one of two basis coherent states, \mbox{$\ket{\pm\alpha}$}. \mbox{$\mathrm{wt}(\vec{x})$} denotes the Hamming weight of bit-string $\vec{x}$. Two states are indistinguishable if their trace distance is 0, and distinguishable (orthogonal) if their trace distance is 1. Lower trace distance between encoded states implies a lower chance of Bob guessing Alice's plaintext input state.} \label{fig:homo_coh_st_tr}
\end{figure}
\else
\begin{figure*}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{coherent_state_homo_unenc}
\includegraphics[clip=true, width=0.475\textwidth]{coherent_state_homo_enc}
\captionspacefig \caption{Trace distance between unencoded (top) and encoded (bottom) basis states for coherent state computation using phase-key encoding, with \mbox{$d=50$} keys and \mbox{$m=10$} modes. Each mode is inputted with one of two basis coherent states, \mbox{$\ket{\pm\alpha}$}. \mbox{$\mathrm{wt}(\vec{x})$} denotes the Hamming weight of bit-string $\vec{x}$. Two states are indistinguishable if their trace distance is 0, and distinguishable (orthogonal) if their trace distance is 1. Lower trace distance between encoded states implies a lower chance of Bob guessing Alice's plaintext input state.} \label{fig:homo_coh_st_tr}
\end{figure*}
\fi

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{coherent_state_homo_ratio}
\captionspacefig \caption{Ratio of the trace distance between unencoded and encoded basis states for coherent state computation using phase-key encoding, with \mbox{$d=50$} keys and \mbox{$m=10$} modes. \mbox{$R<1$} implies information hiding from Bob.} \label{fig:homo_coh_st_ratio}
\end{figure}

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{lo_displacement_homo}
\captionspacefig \caption{Circuit layout for displacement-key homomorphic encoding of passive linear optics, where \mbox{$\alpha_i'=\alpha_i/r$} and \mbox{$\beta_i'=\beta_i/r$}. Mixing the input modes with respective coherent states on a very low-reflectivity ($r$) beamsplitter implements the displacement operations. Following decoding, the output states is simply given by \mbox{$\ket{\psi_\mathrm{out}} = \hat{U}\ket{\psi_\mathrm{in}}$}, the computed input state.}\label{fig:lo_disp_key_circuit}	
\end{figure}

### 2018-09-10 Sections/entanglement_the_ultimate_quantum_resource.tex
Fixed caption dist
Fixed comment positions
Adding image cropping

\if 2\pubmode
	\begin{figure}[!htbp]
		\includegraphics[width=0.475\textwidth]{satellite_downlink_uplink_long}
		\caption{Satellite-mediated cluster state fusion operations for creating a link between two cluster states held by distant ground nodes. (top) Via entanglement distribution over a downlink channel. (bottom) Via distributed Bell projection over an uplink channel. When performing a distributed Bell measurement it is essential that the optical qubits arrive synchronously at the entangling measurement device, denoted \mbox{$\ket{\Psi^+}\bra{\Psi^+}$} (e.g a PBS), which is technologically challenging to implement on satellite given the unpredictable nature of the atmospheric quantum channel, necessitating on-board quantum memories to synchronise the qubits. This is likely to make downlinks cheaper, faster and more efficient than uplinks.} \label{fig:sat_up_down}
	\end{figure}
\else
	\begin{figure*}[!htbp]
		\includegraphics[width=\textwidth]{satellite_downlink_uplink}
		\caption{Satellite-mediated cluster state fusion operations for creating a link between two cluster states held by distant ground nodes. (left) Via entanglement distribution over a downlink channel. (right) Via distributed Bell projection over an uplink channel. When performing a distributed Bell measurement it is essential that the optical qubits arrive synchronously at the entangling measurement device, denoted \mbox{$\ket{\Psi^+}\bra{\Psi^+}$} (e.g a PBS), which is technologically challenging to implement on satellite given the unpredictable nature of the atmospheric quantum channel, necessitating on-board quantum memories to synchronise the qubits. This is likely to make downlinks cheaper, faster and more efficient than uplinks.} \label{fig:sat_up_down}
	\end{figure*}
\fi

>>>>

\if 2\pubmode
	\begin{figure}[!htbp]
		\includegraphics[clip=true, width=0.475\textwidth]{satellite_downlink_uplink_long}
		\captionspacefig \caption{Satellite-mediated cluster state fusion operations for creating a link between two cluster states held by distant ground nodes. (top) Via entanglement distribution over a downlink channel. (bottom) Via distributed Bell projection over an uplink channel. When performing a distributed Bell measurement it is essential that the optical qubits arrive synchronously at the entangling measurement device, denoted \mbox{$\ket{\Psi^+}\bra{\Psi^+}$} (e.g a PBS), which is technologically challenging to implement on satellite given the unpredictable nature of the atmospheric quantum channel, necessitating on-board quantum memories to synchronise the qubits. This is likely to make downlinks cheaper, faster and more efficient than uplinks.} \label{fig:sat_up_down}
	\end{figure}
\else
	\begin{figure*}[!htbp]
		\includegraphics[clip=true, width=\textwidth]{satellite_downlink_uplink}
		\captionspacefig \caption{Satellite-mediated cluster state fusion operations for creating a link between two cluster states held by distant ground nodes. (left) Via entanglement distribution over a downlink channel. (right) Via distributed Bell projection over an uplink channel. When performing a distributed Bell measurement it is essential that the optical qubits arrive synchronously at the entangling measurement device, denoted \mbox{$\ket{\Psi^+}\bra{\Psi^+}$} (e.g a PBS), which is technologically challenging to implement on satellite given the unpredictable nature of the atmospheric quantum channel, necessitating on-board quantum memories to synchronise the qubits. This is likely to make downlinks cheaper, faster and more efficient than uplinks.} \label{fig:sat_up_down}
	\end{figure*}
\fi
